Individual and Differential Harm in Redistricting

### 2022-05-04 paper/paper.Rmd
line
typo

```{r diffharm-minissouri}
#| fig.cap: |
#|      Three potential districting plans for Minissouris: 
#|      a Democratic gerrymander (a), 
#|      a close-to-proportional plan (b), and a Republican gerrymander (c).
#|      Panels (d) and (f) show the total harm to voters in each precinct done 
#|      by their corresponding gerrymander, using (b) as a counterfactual.
#|      Panel (e) summarizes this harm by party and across precincts, showing 
#|      the average harm done to voters of each party by each gerrymander.
include_graphics("figures/diffharm_minissouri.pdf")
```

@@

Motivated primarily by computational convenience, we use a *proportionate uniform shift* model, which focuses on swings in the national political environment as the main determinant of election outcomes.
Each election outcome over the period of interest (generally ten years or less) is modeled as a random deviation from a baseline outcome, and these deviations are assumed to consist of a constant fraction of voters of one party in each precinct switching to the other.
The baseline itself can be established by averaging the results of all available statewide elections over the past decade or other suitable period.
The proportionate uniform shift model is nearly identical to the uniform partisan swing model of @butler1951swing for most precincts and districts, but is more computationally convenient and avoids issues of vote shares exceeding 100% or falling below 0%.
Despite their simplicity, uniform-swing--type models are highly accurate for out-of-sample prediction [@katz2020], and are intuitive and easy to implement.
More details about our proportionate uniform shift model may be found in Appendix \ref{app:formulas}.

>>>>

```{r diffharm-minissouri}
#| fig.cap: |
#|      Three potential districting plans for Minissouri: 
#|      a Democratic gerrymander (a), 
#|      a close-to-proportional plan (b), and a Republican gerrymander (c).
#|      Panels (d) and (f) show the total harm to voters in each precinct done 
#|      by their corresponding gerrymander, using (b) as a counterfactual.
#|      Panel (e) summarizes this harm by party and across precincts, showing 
#|      the average harm done to voters of each party by each gerrymander.
include_graphics("figures/diffharm_minissouri.pdf")
```

@@

Motivated primarily by computational convenience, we use a *proportionate uniform shift* model, which focuses on swings in the national political environment as the main determinant of election outcomes.
Each election outcome over the period of interest (generally ten years or less) is modeled as a random deviation from a baseline outcome, and these deviations are assumed to consist of a constant fraction of voters of one party in each precinct switching to the other.
The baseline itself can be established by averaging the results of all available statewide elections over the past decade or other suitable period.
The proportionate uniform shift model is nearly identical to the uniform partisan swing model of @butler1951swing for most precincts and districts, but is more computationally convenient and avoids issues of vote shares exceeding 100% or falling below 0%.
Despite their simplicity, uniform-swing--type models are highly accurate for out-of-sample prediction [@katz2020], and are intuitive and easy to implement.
More details about our proportionate uniform shift model and how it may be used to efficiently estimate the harm measures may be found in Appendix \ref{app:formulas}.
